---
title: "Data Simulation"
author: "Xiangyi Xu"
date: "Thursday, April 09, 2015"
output:
  html_document:
    keep_md: yes
---
generate_dataset <- function(N=100){
        age <- runif(N, min=72-10, max=72+10)
        
        obesiety <- sample(c("Y", "N"), N, replace=TRUE, prob=c(.36, .64))
        
        sex <- sample(c("M", "F"), N, replace=TRUE, prob=c(.46, .54))
        
        marital_status <- sample(c("Yes", "No"), N, replace=TRUE, prob=c(.70, 
                                    .30))
        diabetes <- sample(c("Y", "N"), replace=TRUE, prob=)
        
        smoking <- sample(c("Never", "Past", "Current"), replace=TRUE, 
                             prob=c(.55, .27, .18))
                             
        diet <- function(){
        
        vitaminC <-                      
        cataract <- function(){
             
        
        }

# add some noise

        zodiac <- c("Aries", "Taurus", "Gemini", "Cancer", "Leo", "Virgo",
                      "Libra","Scorpio", "Sagittarius", "Capricorn","Aquarius", 
                        "Pisces") 
        sign <- sample(zodiac, N, replace=TRUE)
        
        
        
        data.frame(sex, age, obesity, diabetes, smoking, diet, sign, cataract)
}




```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```


